### 2017-03-06 README.Rmd
updated README

>>>>

## Random forest example

As a first example, we'll fit a random forest to the famous Boston housing data included with the package (see `?boston` for details). In fact the original motivation for this package was to be able to compute two-predictor partial dependence plots from random forest models in R. 
```{r, fig.width=8, fig.height=4, message=FALSE}
# Fit a random forest to the Boston housing data
library(randomForest)  # install.packages("randomForest")
data (boston)  # load the boston housing data
set.seed(101)  # for reproducibility
boston.rf <- randomForest(cmedv ~ ., data = boston)

# Partial dependence of cmedv on lstat and rm
library(pdp)
pd <- partial(boston.rf, pred.var = c("lstat", "rm"), chull = TRUE)
head(pd)  # print first 6 rows

# Lattice version
p1 <- plotPartial(pd, main = "lattice version")

# ggplot2 version
library(ggplot2)
p2 <- autoplot(pd, contour = TRUE, title = "ggplot2 version", 
               legend.title = "Partial\ndependence")

# Show both plots in one figure
grid.arrange(p1, p2, ncol = 2)
```

Next, we'll fit a classification model to the Pima Indians Diabetes data.

## Support vector machine (SVM) example

As a second example, we'll fit an SVM to the Pima Indians diabetes data included with the package (see `?pima` for details). Note that for some fitted model objects (e.g., `"ksvm"` objects) it is necessary to supply the original training data via the `train` argument in the call to `partial`.

```{r, fig.width=8, fig.height=4, message=FALSE}
# Fit an SVM to the Pima Indians diabetes data
library(kernlab)  # install.packages("kernlab")
data (pima)  # load the Pima Indians diabetes data
pima.svm <- ksvm(diabetes ~ ., data = pima, type = "C-svc", kernel = "rbfdot",
                 C = 0.5, prob.model = TRUE)

# Partial dependence of diabetes test result on glucose (default is logit scale)
pd.glucose <- partial(pima.svm, pred.var = "glucose", train = pima)

# Partial dependence of diabetes test result on glucose (probability scale)
pd.glucose.prob <- partial(pima.svm, pred.var = "glucose", prob = TRUE, 
                           train = pima)

# Show both plots in one figure
grid.arrange(autoplot(pd.glucose, title = "Logit scale"), 
             autoplot(pd.glucose.prob, title = "Probability scale"), 
             ncol = 2)
```
